%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Aira Jena} \\ \vspace{1pt}
    Patia, Bhubaneswar, Odisha 751024 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 8917395148 ~ \href{mailto:0xaira.eth@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{0xaira.eth}} ~ 
    \href{https://linkedin.com/in/aira-jena/}{\raisebox{-0.2\height}\faLinkedin\ \underline{aira-jena}}  ~
    \href{https://linkedin.com/in/aira-jena/}{\raisebox{-0.2\height}\faTwitter\ \underline{0xAira}} ~
    \href{https://github.com/0xaira}
    {\raisebox{-0.2\height}\faGithub\ \underline{0xaira}} ~
    \href{https://github.com/0xaira}
    {\raisebox{-0.2\height}\faGlobe\ \underline{0xaira}}
    \vspace{-8pt}
\end{center}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oxford College of Engineering}{Nov. 2022 -- May 2026}
      {Bachelor of Technology in Computer Science}{Bhubaneshwar, Odisha}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Blockchain Technology
                \item Algorithms Analysis
                \item Database Management
                \item Artificial Intelligence
                \item Internet Technology
                \item Systems Programming
                \item Computer Architecture
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {LearnWeb3DAO}{May 2022 -- August 2022}
      {Blockchain Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Cleared Freshman level , with Solidity and Basic of Blockchain , ERC20 , ERC721.}
        \resumeItem{Completed Sophomore level in Web3 with knowledge in tech like POW , EVM , GAS , DApp, ICO , NFT collection , DAO and DEX exchange.}
        \resumeItem{Completed Junior level in Web3 with knowledge of technologies like Layer2 , ENS , Chain link , Graph , IPFS , CERAMIC.}
        \resumeItem{Completed Senior level in Web3 with proficiency in Technologies like Smart Contract Security , Merkle Trees , Flash Loan , MEV , Flashbots , Gasless transaction and Smart contract Upgradability.}
        \resumeItem{ Senior Graduate in Web3 from LearnWeb3DAO , with knowledge in field of Smart Contracts and Security , Solidity , DApp , NFT , DAO , DEX and Advanced Blockchain Concepts . Worked on protocol like Graph, Chainlink , IPFS and Aave .}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Supply Chain dApp} $|$ \emph{Solidity, React.js Web3.js} $|$ \href{}{WebApp} $|$ \href{}{Github}}{January 2023}
          \resumeItemListStart
            \resumeItem{Used Solidity to write the Supply Chain Smart Contracts which is then compiled, migrated and deployed using Truffle.js on the local blockchain network created using Ganache-cli.}
            \resumeItem{ Used Web3.js to communicate with the smart contract and local blockchain network}
            \resumeItem{Used React.js framework to build Supply chain frontend for better component and state lifecycle management.}
            \resumeItem{Used Nginx(load balancer) to forward requests to frontend and used Express.js for dynamic routing.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Decentralized Voting App} $|$ \emph{Solidity, React.js, Next.js} $|$ \href{}{WebApp} $|$ \href{}{Github}}{November 2022}
          \resumeItemListStart
            \resumeItem{Created a Voting dApp using Solidity to write the smart contracts and Hardhat for testing and and deploying them to main net.}
            \resumeItem{Used React.js and Next.js for blockchain application with smart contract, context API for state management .}
            \resumeItem{Used Web3.js to communicate with the smart contract and local blockchain network.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Play To Earn(P2E) Game} $|$ \emph{ThirdWeb, Next.js, Typescipt, Solidity} $|$ \href{}{WebApp} $|$ \href{}{Github}}{October 2022}
          \resumeItemListStart
            \resumeItem{Created full crypto based Play To Earn Game using ThirdWeb, Next.js, Typescipt and Solidity .}
            \resumeItem{Deployed NFTs Collection and created Edition Drop Contract, Mining Contract, Token Contract for characters of game using Thirdweb SDK.}
            \resumeItem{Built the frontend with Next.js and Typescipt to improve the developer experience}
            
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C++, HTML/CSS, JavaScript, SQL, Rust} \\
     \textbf{Developer Tools}{: VS Code, Google Cloud Platform, Remix IDE, } \\
     \textbf{Technologies/Frameworks}{: Linux, GitHub, React, Next, Express, Ganache, Truffle, Web3.js, Node, Docker } \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Y Combinator(Forage)}{August-2022}{Full Stack Intern}{Remote}
            \resumeItemListStart
                \resumeItem{Added new feature, the kanban board, to move shipping requests, to two new lane statuses (in-progress and complete).}
                \resumeItem{ Added few functions that take the user event on the frontend and then save it to your database..}
                \resumeItem{Created insights and ideas backed by data obtained after analysing the latest feature releases.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
